LLM-Driven CIDOC-CRM Knowledge Graph Extraction from Museum Archives

### 2025-05-02 paper/paper.tex
paper: fix hanging sentence
paper: mention dataset size, JSON parse, valid triplet %

The museum's official public website contains a wealth of information about its collection, with many exhibits and artifacts having dedicated articles. These articles were used to construct a dataset of textual information from the museum's collection, with each entry representing a complete article dedicated to a particular item.

@@

\begin{enumerate}
    \item Ontology Verbalization: The ontology is verbalized into a natural language description. We use the 24037 Erlangen CRM implementation of CIDOC-CRM 7.1.3.
    \item System Prompt Construction: A system prompt is constructed from the following elements:
          \begin{itemize}
              \item A clear task description instructing the LLM to extract entities and relationships from the input text and represent them as a knowledge graph adhering to the provided ontology.
              \item Examples demonstrating desired output format.
              \item The verbalized ontology, appended at the end of the system prompt.
          \end{itemize}
    \item Chat History Initialization: The chat history is initialized with an example input and output to serve as an in-context learning mechanism.
    \item Triplet Extraction: The system prompt, chat history and text chunk are sent to the LLM. The response is parsed as a list of triplets.
\end{enumerate}

@@

The KBQA task was executed by constructing a system prompt. For the ontology-guided and ontology-free knowledge graphs, the prompt included a verbalized representation of the respective graph as the primary context, instructing the LLM to answer each multiple-choice question (with options "A", "B", "C", or "D") using only the information provided in the context. Meanwhile, the no-context baseline prompt simply presented the question to the LLM without any additional context. The score for each question

@@

\begin{table}[h]
    \centering
    \caption{Ontology Conformance}
    \label{tab:oc_percent}
    \begin{tabular}{|l|c|c|c|}
        \hline
        Graph       & Total Triplets & Valid Triplets & Score          \\
        \hline
        Qwen 2.5 3B & 364            & 177            & 48.63          \\
        \hline
        Llama 3 3B  & 417            & 218            & 52.28          \\
        \hline
        Qwen 2.5 7B & 443            & 225            & 50.79          \\
        \hline
        Llama 3 8B  & 519            & 332            & 63.97          \\
        \hline
        DeepSeek V3 & 630            & 596            & 94.6           \\
        \hline
        DeepSeek R1 & 630            & 622            & \textbf{98.73} \\
        \hline
    \end{tabular}
\end{table}

>>>>

The museum's official public website contains a wealth of information about its collection, with many exhibits and artifacts having dedicated articles. These articles were used to construct a dataset of textual information from the museum's collection. We collected 40 such articles such that each entry of the dataset represented a complete article dedicated to a particular item.

@@

\begin{enumerate}
    \item Ontology Verbalization: The ontology is verbalized into a natural language description. We use the 24037 Erlangen CRM implementation of CIDOC-CRM 7.1.3.
    \item System Prompt Construction: A system prompt is constructed from the following elements:
          \begin{itemize}
              \item A clear task description instructing the LLM to extract entities and relationships from the input text and represent them as a knowledge graph adhering to the provided ontology.
              \item Examples demonstrating desired output format.
              \item The verbalized ontology, appended at the end of the system prompt.
          \end{itemize}
    \item Chat History Initialization: The chat history is initialized with an example input and output to serve as an in-context learning mechanism.
    \item Triplet Extraction: The system prompt, chat history and text chunk are sent to the LLM. The response is parsed as a JSON list of triplets.
\end{enumerate}

@@

The KBQA task was executed by constructing a system prompt. For the ontology-guided and ontology-free knowledge graphs, the prompt included a verbalized representation of the respective graph as the primary context, instructing the LLM to answer each multiple-choice question (with options "A", "B", "C", or "D") using only the information provided in the context. Meanwhile, the no-context baseline prompt simply presented the question to the LLM without any additional context.

@@

\begin{table}[h]
    \centering
    \caption{Ontology Conformance}
    \label{tab:oc_percent}
    \begin{tabular}{|l|c|c|c|}
        \hline
        Graph       & Total Triplets & Valid Triplets & Valid Triplets (\%) \\
        \hline
        Qwen 2.5 3B & 364            & 177            & 48.63               \\
        \hline
        Llama 3 3B  & 417            & 218            & 52.28               \\
        \hline
        Qwen 2.5 7B & 443            & 225            & 50.79               \\
        \hline
        Llama 3 8B  & 519            & 332            & 63.97               \\
        \hline
        DeepSeek V3 & 630            & 596            & 94.6                \\
        \hline
        DeepSeek R1 & 630            & 622            & \textbf{98.73}      \\
        \hline
    \end{tabular}
\end{table}
